\documentclass[12pt, letterpaper]{article}
\usepackage{graphicx}
\usepackage[table]{xcolor}
\usepackage{array,booktabs,ragged2e}
\usepackage{hyperref}
\usepackage{enumitem}
\graphicspath{{images/}}

\title{\textbf{Game Design Document}}
\author{Elicatza}
\date{July 2024}

\newcolumntype{R}[1]{>{\RaggedLeft\arraybackslash}p{#1}}
\setcounter{secnumdepth}{0}

\begin{document}
\maketitle
\tableofcontents
\section{Introduction}

My submission for the 
\href{https://itch.io/jam/pirate}{Pirate Software game jam 2024}.

\subsection{Summary}
Cube managing internal alchemy in a puzzling and shadowy world.

\subsection{Theme interpretation}

The themes are \textit{Alchemy and Shadows}. I'm choosing to interpret alchemy
in the direction of transformations. Specifically internal alchemy.

In regards to shadows, forceful isolation --- an undesired retreat from social
life --- will be my interpretation. Contrast between light and dark will be
employed with shadows to emphasise this effect. The players goal is to escape
from the shadows.

My hopes with shadows is to be able to showcase the turning point when
isolation no longer remains sufficient. Like Zarathustra, there comes a time
for sharing your blossoming soul. Though this is highly unrealistic that I
accomplish this.

\subsection{Inspiration}

Not familiar with other games, but theme is inspired by Spinoza.

\subsection{Software}
\begin{itemize}[itemsep=1pt]
    \item Raylib C
    \item Emscripten
    \item Aseprite
    \item NeoVim
\end{itemize}

\subsection{Target Audience}

Myself.

\subsection{Gameplay}

Life is a puzzle. The gameplay should reflect that.
From completing them, you gain an understanding of the world and
therefore yourself.

The player will be presented with several puzzles / actions. When completing
tasks, the player learns how the character responds. Mostly bad. A pain and
energy meter is what governs what actions are possible. You'll have to balance
pain, energy and socialization. As a game maker I want the player to seek out
socialization, which will progress the game, but causes fatigue and pain.
Shadow and fatigue are equal. Pain represents all other ways of being hurt.

Puzzles that improve health and energy, will be boring, but necessary to
achieve development. Downtime like this should invoke the player to think. The
actions that cause development hurts you. Very \textit{Tao Te Ching} if you
will. Solving the mystery.

\subsection{Mechanics}

You are a cube. Glide around with arrow keys (wasd). Roll around with shift +
arrow keys (wasd). Rolling (shift|u) causes pain. The ground will have
different heights, forcing the player to roll. 

During activities (puzzles), you'll have the additional ability to split the
cube and causing pain. The other option is to mirror shape across line.

\subsection{Story}

Transition your way of life.

\section{Art}

I've used the trans colors because it was largely influential at that time in
my life.

\section{Roadmap}

\bgroup
\def\arraystretch{1.5}
\begin{tabular}{ R{0.4cm} p{4cm} p{1.5cm} p{5.5cm} }
\toprule
\multicolumn{1}{l}{\textbf{\#}} & \textbf{Assignment} & \textbf{Date} & \textbf{Notes} \\ 
\midrule
1 & Write roadmap & 07-17 & Basic overview of steps \\
2 & Write GDD & 07-17 & Figure out themes and content \\
3 & Basic build & 07-18 & C + Emscripten + Raylib fun \\
4 & Quick puzzle demo & 07-21 & ``Quick'' they said \\
5 & Puzzle formats & 07-21 & Byte array spec \\
6 & Environment format & 07-23 & Embedded file format \\
7 & Design environment & 07-25 & Where the player moves \\
8 & Basic lighting & 07-25 & It Makes you see stuff \\
9 & Design basic hud & 07-25 & User feedback \\
10 & Integrate features & 07-26 & It's a game \\
11 & All intractable & 07-27 & Interact with everything \\
12 & Window blinds & 07-28 & Control environment \\
13 & Player faces & 07-28 & It's a cube \\
14 & Design assets & 07-28 & The look \\
15 & Boss fight! & 07-28 & It's a door \\
16 & Light mechanic & 07-29 & Final dimension \\
17 & Time mechanic & 07-29 & Final, final dimension \\
18 & title & 07-30 & Transition \#3 \\
19 & UI & 07-30 & Start, pause, end \& status \\
20 & Display keys & 07-30 & Bad solution \\
21 & Make training puzzles & 07-30 & 20 should be enough \\
22 & Make fun puzzles & 07-31 & 10 of them \\
23 & Make boss puzzles & 07-31 & 10 of them \\
24 & Balancing & 07-31 & Give user ``good'' incentives \\
25 & Fix bugs & 07-31 & Got most of them \\
26 & GDD update & 07-31 & Gameplay overview \\

X & Export GDD & 07-31 & Don't have gdoc, so html \\
X & Submit & TODO & And we're off \\

\bottomrule
\end{tabular}
\egroup

\section{Future development}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{ R{0.4cm} p{4cm} p{1.5cm} p{5.5cm} }
\toprule
\multicolumn{1}{l}{\textbf{\#}} & \textbf{Assignment} & \textbf{Date} & \textbf{Notes} \\ 
\midrule

X & Story & TODO & Write story \\
X & Feedback & TODO & user feedback without graphs \\
X & Audio & TODO & Voice lines + birds \\
X & Animations & TODO & rotate, fade, etc. \\
X & Teach & TODO & Learn keys naturally \\
X & Balancing & TODO & It's very linear \\

\bottomrule
\end{tabular}
\egroup

% Known issues
% Higher contrast in puzzle
% Height not set in puzzle on init

% Fixed
% Player face not changing in puzzle (bad patch)
% Move (input) during sleep
% Shader only draws textures color, not shapes

\end{document}
